Detecting Fair Queuing to Enable Better Congestion Control

### 2020-10-05 paper/paper.tex
Change paper and presentation

@@

%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Anonymous authors}
%
\authorrunning{Anonymous authors}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\author{Maximilian Bachl\inst{1}\orcidID{0000-0001-9482-7428} \and
%Joachim Fabini\inst{2,3}\orcidID{0000-0002-8285-1591} \and
%Tanja Zseby\inst{3}\orcidID{0000-0002-5391-467X}}
%%
%\authorrunning{M. Bachl et al.}
%% First names are abbreviated in the running head.
%% If there are more than two authors, 'et al.' is used.
%%
%\institute{TU Wien, Vienna, Austria; 
%\email{firstname.lastname@tuwien.ac.at}}
%
\maketitle              % typeset the header of the contribution
%

@@

To make our work reproducible and to encourage further research, we make the code, the results and the figures publicly available\footnote{\url{https://github.com/CN-TU/PCC-Uspace}}.

>>>>

\def\anonymize{yes}
\def\tempYes{yes}
\def\tempNo{no}

@@

%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\ifx\anonymize\tempYes
\author{Anonymous authors}
%
\authorrunning{Anonymous authors}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\else
\author{Maximilian Bachl\inst{1}\orcidID{0000-0001-9482-7428} \and
Joachim Fabini\inst{2,3}\orcidID{0000-0002-8285-1591} \and
Tanja Zseby\inst{3}\orcidID{0000-0002-5391-467X}}
%
\authorrunning{M. Bachl et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{TU Wien, Vienna, Austria; 
\email{firstname.lastname@tuwien.ac.at}}
\fi

\maketitle              % typeset the header of the contribution

@@

To make our work reproducible and to encourage further research, we make the code, the results and the figures publicly available\footnote{\ifx\anonymize\tempYes $\langle$anonymized$\rangle$\else\url{https://github.com/CN-TU/PCC-Uspace}\fi}.

### 2020-10-05 paper/presentation.tex
Change paper and presentation

\begin{frame}{Delay- vs.~Loss-based}
\begin{block}{Insight:}
When loss-based and delay-based congestion control compete, loss-based one eats delay-based one's lunch!\end{block}
\end{frame}

@@

\begin{frame}{Summary}
\begin{itemize}
\item Delay-based congestion control offers same throughput but lower delay than loss-based ones
\item When competing, loss-based flows will gain all bandwidth. Delay-based flows ``starve''. 
\item Fair queuing solves this
\end{itemize}
\begin{block}{Insight:}
If flows could detect the presence of fair queuing, they could switch to delay-based congestion control!
\end{block}
\end{frame}

\section{Concept}
\begin{frame}{Overall Algorithm}
\begin{enumerate}
\item During flow startup, determine if fair queuing is used at the bottleneck or not.
\item If this is determined, change to a delay-based congestion control algorithm if fair queuing is used and to a loss-based one otherwise.
\end{enumerate}
\end{frame}

\begin{frame}{Fair queuing detection algorithm}
\begin{enumerate}
\item Launch two concurrent flows, flow 1 and flow 2. Initialize flow 1 with some starting sending rate and flow 2 with two times that rate. 
\item After every delay, if no packet loss occurred, double the sending rate of both flows. 
\item If packet loss occurred in both flows in the previous delay, calculate the following metric if each flow got an equal share of bandwidth (fair queuing) or not (no fair queuing).
\end{enumerate}
\end{frame}

>>>>

\begin{frame}{Delay- vs.~Loss-based}
\begin{block}{Insight:}
When loss-based and delay-based congestion control compete, loss-based gets no bandwidth!\end{block}
\end{frame}

@@

\begin{frame}{Summary}
\begin{itemize}
\item Delay-based congestion control offers same throughput but lower delay than loss-based ones
\item When competing, loss-based flows will gain all bandwidth. Delay-based flows ``starve''
\item Fair queuing solves this
\end{itemize}
\begin{block}{Insight:}
If flows could detect the presence of fair queuing, they could switch to delay-based congestion control!
\end{block}
\end{frame}

\section{Concept}
\begin{frame}{Overall Algorithm}
\begin{enumerate}
\item During flow startup, determine if fair queuing is used at the bottleneck or not
\item If this is determined, change to a delay-based congestion control algorithm if fair queuing is used and to a loss-based one otherwise
\end{enumerate}
\end{frame}

\begin{frame}{Fair queuing detection algorithm}
\begin{enumerate}
\item Launch two concurrent flows, flow 1 and flow 2. Initialize flow 1 with some starting sending rate and flow 2 with two times that rate
\item After every delay, if no packet loss occurred, double the sending rate of both flows
\item If packet loss occurred in both flows in the previous delay, calculate the following metric if each flow got an equal share of bandwidth (fair queuing) or not (no fair queuing)
\end{enumerate}
\end{frame}
